A generalized definition of multidimensional item response theory parameters

### 2023-02-21 output/paper_draft/paper_M2PLM_parameters.Rmd
Drops the use of the term "Euclidean" (not used in the whole paper)

**Proposition 2** Let's consider another basis $`r ALT_BASIS_EQ`$ in
$`r LATENT_SPACE`$ and the inner product $`r ALT_BASIS_INNER_PROD`$ that keeps
the norm of the Euclidean space invariant.

>>>>

**Proposition 2** Let's consider another basis $`r ALT_BASIS_EQ`$ in
$`r LATENT_SPACE`$ and the inner product $`r ALT_BASIS_INNER_PROD`$ that keeps
the norm of the space invariant.
